---
title: "Alcohol vs Seat choice"
author: "Citlali Gonzalez"
date: "6/4/24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
# Introduction
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
you choose to sit in??

The data came from UCDavis in the year 

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

# Methods 
In the data set davisdata Seat is a categorical variable, alcohol is numerical

We try to predict alcohol ~ Seat so we use the numerical ~ categorical helper file. 

# Results

## Descriptive Results

### Graphical Summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

This boxplot shows that the students who sat in the back row were more likely to drink alcohol than the students who sit closer to the front. 

### Numerical Summary

```{r}
favstats(momheight~Sex,data=ucdavis1)
```

The numerical summary shows that Females have a lower mean than the males.

### Inferential Results

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is 0.000116, less than 0.05 so we reject null hypothesis
There is a difference in alcohol consumption based in where people sit

```{r}
plot(TukeyHSD(model1))
```
The boxplot shows the difference in mean levels of the seats.
    
## Conclusions

I conclude that students who sit in the back are more likely to drink alcohol than the students who sit in the front. The females have a lower mean than the males.

